Typesafe Coordinate Systems in High-Throughput Sequencing Applications

### 2022-02-23 manuscript/main.tex
added rust example to manuscript
edited D example in manuscript

\begin{verbatim}
    Interval <CoordSystem::zbho> i (0, 100);    // C++
    auto i = Interval!CoordSystem.zbho(0, 100); // D
\end{verbatim}

@@

\begin{verbatim}
    auto i = ZBHO(0, 100);  // [0, 100) (zero-based)
    auto j = OBC(1, 100);   // [1, 100] (one-based)
    auto k = i.to!CoordSystem.obc;
    assert(k == j);
\end{verbatim}

>>>>

\begin{verbatim}
    Interval <CoordSystem::zbho> i (0, 100);    // C++
    auto i = Interval!CoordSystem.zbho(0, 100); // D
    let i = Interval::<ZeroBased, HalfOpen>::from_int(0, 100); // rust
\end{verbatim}

@@

\begin{verbatim}
    auto i = ZBHO(0, 100);  // [0, 100) (zero-based)
    auto j = OBC(1, 100);   // [1, 100] (one-based)
    auto k = i.to!OBC;
    assert(k == j);
\end{verbatim}
